\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2018-02-15 paper_pt-br.tex
Update paper_pt-br.tex

\section{The Bitcoin Blockchain Scalability Problem}

@@

To achieve much higher than 47,000 transactions per second using Bitcoin
requires conducting transactions off the Bitcoin blockchain itself. It would be
even better if the bitcoin network supported a near-unlimited number of
transactions per second with extremely low fees for micropayments. Many
micropayments can be sent sequentially between two parties to enable any size
of payments. Micropayments would enable unbundling, less trust and
commodification of services, such as payments for per-megabyte Internet
service. To be able to achieve these micropayment use cases, however, would
require severely reducing the amount of transactions that end up being
broadcast on the global Bitcoin blockchain.

@@

If we presume a large network of channels on the Bitcoin blockchain, and all
Bitcoin users are participating on this graph by having at least one channel
open on the Bitcoin blockchain, it is possible to create a near-infinite amount
of transactions inside this network. The only transactions that are broadcast
on the Bitcoin blockchain prematurely are with uncooperative channel
counterparties.

%TODO: define hashlock and timelock
By encumbering the Bitcoin transaction outputs with a hashlock and timelock,
the channel counterparty will be unable to outright steal funds and bitcoins
can be exchanged without outright counterparty theft. Further, by using
staggered timeouts, it's possible to send funds via multiple intermediaries in a
network without the risk of intermediary theft of funds.

@@

Mark Friedenbach has proposed that Sequence Numbers can be enforcible via a
relative block maturity of the parent transaction via a
soft-fork\cite{seqnum}. This would allow some basic ability to ensure some form
of relative block confirmation time lock on the spending script. In addition, an
additional opcode, OP\_CHECKSEQUENCEVERIFY\cite{csv} (a.k.a.
OP\_RELATIVECHECKLOCKTIMEVERIFY)\cite{relCLTV}, would permit further abilities,
including allowing a stop-gap solution before a more permanent solution for
resolving transaction malleability. A future version of this paper will include
proposed solutions.

@@

Similar to RSMCs, these contract terms are programatically enforced on the
Bitcoin blockchain and do not require trust in the counterparty to adhere to the
contract terms, as all violations are penalized via unilaterally enforced
fidelity bonds, which are constructed using penalty transactions spending from
commitment states. If Bob knows $R$ within three days, then he can redeem the
funds by broadcasting a transaction; Alice is unable to withhold the funds in
any way, because the script returns as valid when the transaction is spent on
the Bitcoin blockchain.

@@

It is within both parties individual responsibility to ensure that they can get
their transaction into the blockchain in order to ensure the balances are
correct. For Bob, in order to receive the funds, he must either broadcast the
``Delivery'' transaction on the Bitcoin blockchain, or otherwise settle with
Alice (while canceling the HTLC). For Alice, she must broadcast the ``Timeout''
3 days from now to receive the refund, or cancel the HTLC entirely with Bob.

@@

It is preferable to use a small payment per HTLC. One should not use an
extremely high payment, in case the payment does not fully route to its
destination. If the payment does not reach its destination and one of the
participants along the path is uncooperative, it is possible that the sender
must wait until the expiry before receiving a refund. Delivery may be lossy,
similar to packets on the Internet, but the network cannot outright steal funds
in transit. Since transactions don't hit the blockchain with cooperative channel
counterparties, it is recommended to use as small of a payment as possible. A
trade off exists between locking up transaction fees on each hop versus the
desire to use as small a transaction amount as possible (the latter of which may
incur higher total fees). Smaller transfers with more intermediaries imply a
higher percentage paid as Lightning Network fees to the intermediaries.

@@

\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1\linewidth]{figures/network-fig3.pdf}
	}
	\caption{Dave creates a path back to Alice after Alice fails to send
		funds to Dave, because Carol is uncooperative. The input R from
		hash(R) is never broadcast by Dave, because Carol did not
		complete her actions. If R was broadcast, Alice will
		break-even. Dave, who controls R should never broadcast R
		because he may not receive funds from Carol, he should let the
		contracts expire. Alice and Bob have the option to net out and
		close the contract early, as well, in this diagram.
	}
\end{figure}

@@

Forced expiration of many transactions may be the greatest systemic risk when
using the Lightning Network. If a malicious participant creates many channels
and forces them all to expire at once, these may overwhelm block data capacity,
forcing expiration and broadcast to the blockchain. The result would be mass
spam on the bitcoin network. The spam may delay transactions to the point where
other timelocked transactions become valid.

@@

The risk model of this attack occurring is similar to that of miners colluding
to do reorg attacks: Extremely unlikely with many uncoordinated miners.

@@

	\item Micropayments. Bitcoin blockchain fees are far too high to accept
		micropayments, especially with the smallest of values. With this
		system, near-instant micropayments using Bitcoin without a 3rd
		party custodian would be possible. It would enable, for example,
		paying per-megabyte for Internet service or per-article to read
		a newspaper.

@@

	\item Cross-Chain Payments. So long as there are similar hash-functions
		across chains, it's possible for transactions to be routed over
		multiple chains with different consensus rules. The sender does
		not have to trust or even know about the other chains -- even
		the destination chain. Similarly, the receiver does not have to
		know anything about the sender's chain or any other chain. All
		the receiver cares about is a conditional payment upon
		knowledge of a secret on their chain. Payment can be routed by
		participants in both chains in the hop. E.g. Alice is on
		Bitcoin, Bob is on both Bitcoin and X-Coin and Carol is on
		a hypothetical X-Coin, Alice can pay Carol without
		understanding the X-Coin consensus rules.

@@

\section{Acknowledgments}

>>>>

\section{O problema de escalabilidade do bitcoin}

@@

To achieve much higher than 47,000 transactions per second using Bitcoin
requires conducting transactions off the Bitcoin blockchain itself. It would be
even better if the bitcoin network supported a near-unlimited number of
transactions per second with extremely low fees for micropayments. Many
micropayments can be sent sequentially between two parties to enable any size
of payments. Micropayments would enable unbundling, less trust and
commodification of services, such as payments for per-megabyte internet
service. To be able to achieve these micropayment use cases, however, would
require severely reducing the amount of transactions that end up being
broadcast on the global Bitcoin blockchain.

@@

If we presume a large network of channels on the Bitcoin blockchain, and all
Bitcoin users are participating on this graph by having at least one channel
open on the Bitcoin blockchain, it is possible to create a near-infinite amount
of transactions inside this network. The only transactions that are broadcasted
on the Bitcoin blockchain prematurely are with uncooperative channel
counterparties.

%TODO: define hashlock and timelock
By encumbering the Bitcoin transaction outputs with a hashlock and timelock,
the channel counterparty will be unable to outright steal funds and Bitcoins
can be exchanged without outright counterparty theft. Further, by using
staggered timeouts, it's possible to send funds via multiple intermediaries in a
network without the risk of intermediary theft of funds.

@@

Mark Freidenbach has proposed that Sequence Numbers can be enforcible via a
relative block maturity of the parent transaction via a
soft-fork\cite{seqnum}. This would allow some basic ability to ensure some form
of relative block confirmation time lock on the spending script. In addition, an
additional opcode, OP\_CHECKSEQUENCEVERIFY\cite{csv} (a.k.a.
OP\_RELATIVECHECKLOCKTIMEVERIFY)\cite{relCLTV}, would permit further abilities,
including allowing a stop-gap solution before a more permanent solution for
resolving transaction malleability. A future version of this paper will include
proposed solutions.

@@

Similar to RSMCs, these contract terms are programatically enforced on the
Bitoin blockchain and do not require trust in the counterparty to adhere to the
contract terms, as all violations are penalized via unilaterally enforced
fidelity bonds, which are constructed using penalty transactions spending from
commitment states. If Bob knows $R$ within three days, then he can redeem the
funds by broadcasting a transaction; Alice is unable to withhold the funds in
any way, because the script returns as valid when the transaction is spent on
the Bitcoin blockchain.

@@

It is within both parties individual responsibility to ensure that they can get
their transaction into the blockchain in order to ensure the balances are
correct. For Bob, in order to receive the funds, he must either broadcast the
``Delivery'' transaction on the Bitcoin blockchain, or otherwise settle with
Alice (while cancelling the HTLC). For Alice, she must broadcast the ``Timeout''
3 days from now to receive the refund, or cancel the HTLC entirely with Bob.

@@

It is preferable to use a small payment per HTLC. One should not use an
extremely high payment, in case the payment does not fully route to its
destination. If the payment does not reach its destination and one of the
participants along the path is uncooperative, it is possible that the sender
must wait until the expiry before receiving a refund. Delivery may be lossy,
similar to packets on the internet, but the network cannot outright steal funds
in transit. Since transactions don't hit the blockchain with cooperative channel
counterparties, it is recommended to use as small of a payment as possible. A
tradeoff exists between locking up transaction fees on each hop versus the
desire to use as small a transaction amount as possible (the latter of which may
incur higher total fees). Smaller transfers with more intermediaries imply a
higher percentage paid as Lightning Network fees to the intermediaries.

@@

\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1\linewidth]{figures/network-fig3.pdf}
	}
	\caption{Dave creates a path back to Alice after Alice fails to send
		funds to Dave, because Carol is uncooperative. The input R from
		hash(R) is never brodcast by Dave, because Carol did not
		complete her actions. If R was broadcast, Alice will
		break-even. Dave, who controls R should never broadcast R
		because he may not receive funds from Carol, he should let the
		contracts expire. Alice and Bob have the option to net out and
		close the contract early, as well, in this diagram.
	}
\end{figure}

@@

Forced expiration of many transactions may be the greatest systemic risk when
using the Lightning Network. If a malicious participant creates many channels
and forces them all to expire at once, these may overwhelm block data capacity,
forcing expiration and broadcast to the blockchain. The result would be mass
spam on the bitcoin network. The spam may delay transactions to the point where
other locktimed transactions become valid.

@@

The risk model of this attack occurirng is similar to that of miners colluding
to do reorg attacks: Extremely unlikely with many uncoordinated miners.

@@

	\item Micropayments. Bitcoin blockchain fees are far too high to accept
		micropayments, especially with the smallest of values. With this
		system, near-instant micropayments using Bitcoin without a 3rd
		party custodian would be possible. It would enable, for example,
		paying per-megabyte for internet service or per-article to read
		a newspaper.

@@

	\item Cross-Chain Payments. So long as there are similar hash-functions
		across chains, it's possible for transactions to be routed over
		multiple chains with different consensus rules. The sender does
		not have to trust or even know about the other chains -- even
		the destination chain. Simiarly, the receiver does not have to
		know anything about the sender's chain or any other chain. All
		the receiver cares about is a conditional payment upon
		knowledge of a secret on their chain. Payment can be routed by
		participants in both chains in the hop. E.g. Alice is on
		Bitcoin, Bob is on both Bitcoin and X-Coin and Carol is on
		a hypothetical X-Coin, Alice can pay Carol without
		understanding the X-Coin consensus rules.

@@

\section{Acknowledgements}
